%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Stylish Curriculum Vitae
% LaTeX Template
% Version 1.0 (18/7/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Stefano (http://stefano.italians.nl/)
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% The main font used in this template, Adobe Garamond Pro, does not 
% come with Windows by default. You will need to download it in
% order to get an output as in the preview PDF. Otherwise, change this 
% font to one that does come with Windows or comment out the font line 
% to use the default LaTeX font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letter, oneside, final]{scrartcl} % Paper options using the scrartcl class

\usepackage{scrpage2} % Provides headers and footers configuration
\usepackage{titlesec} % Allows creating custom \section's
\usepackage{marvosym} % Allows the use of symbols
\usepackage{tabularx,colortbl} % Advanced table configurations
\usepackage{fontspec} % Allows font customization
\usepackage{ragged2e} % For justifying text

\defaultfontfeatures{Mapping=tex-text}
\setmainfont{Adobe Garamond Pro} % Main document font

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule] % Section formatting

\pagestyle{scrheadings} % Print the headers and footers on all pages

\addtolength{\voffset}{-0.5in} % Adjust the vertical offset - less whitespace at the top of the page
\addtolength{\textheight}{3cm} % Adjust the text height - less whitespace at the bottom of the page

\newcommand{\gray}{\rowcolor[gray]{.90}} % Custom highlighting for the work experience and education sections

%----------------------------------------------------------------------------------------
% FOOTER SECTION
%----------------------------------------------------------------------------------------

\renewcommand{\headfont}{\normalfont\rmfamily\scshape} % Font settings for footer

\cofoot{
\addfontfeature{LetterSpace=20.0}\fontsize{12.5}{17}\selectfont % Letter spacing and font size

Paseo Ensenada 1527, Playas de Tijuana {\large\textperiodcentered} Tijuana {\large\textperiodcentered} México % Your mailing address
{\Large\Letter} chuyespinoza@gmail.com \ {\Large\Telefon} (664) 110-9697 % Your email address and phone number
}

%----------------------------------------------------------------------------------------

\begin{document}

\begin{center} % Center everything in the document

%----------------------------------------------------------------------------------------
% HEADER SECTION
%----------------------------------------------------------------------------------------

{\addfontfeature{LetterSpace=20.0}\fontsize{26}{26}\selectfont\scshape Jes\'us Espinoza Hern\'andez} % Your name at the top

\vspace{1cm} % Extra whitespace after the large name at the top

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\section{About Me}
\justifying{
Accomplished Senior Software Specialist with 11 years of experience architecting and implementing end-to-end solutions in the medical, semiconductor and telecom industry. I am self taught and highly motived to learn new technologies and improve my skills.

3 years experience developing data pre-processing architectures and applications in the telecom industry. I have worked for large companies such as Verizon and NTT developing data mediation solutions for large scale distributed systems.

4 years experience developing web applications for the medical imaging industry using Java technologies and the medical standards DICOM and HL7. My projects where implemented in various radiology clinics as an employee and large government institutions such as Mexico's ISSSTE as a freelancer. These projects consisted mainly of image acquisition from X-Ray machines, image storage and presentation, as well as general department workflows such as patient scheduling and reporting.

4 years experience developing data extraction, post-processing and reporting applications in the semiconductor industry. These consisted of automating the extraction of data logs from test machines and then parsing, analyzing and reporting using Python technologies.

}


%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\section{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Python, SQL, Java, C\#, Swift \\
Protocols \& APIs & DICOM, JavaEE 7, Spring, iOS Development \\
Databases & MySQL, Oracle 11g \\
Tools & Git, Linux, Docker, Wildfly Application Server \\
& MediationZone from DigitalRoute \\
Other & Amazon Web Services
\end{tabular}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Work Experience}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
	\gray Period & \textbf{February 2014 --- February 2017}\\
	\gray Employer & \textbf{AgileTransactions}\\
	\gray Job Title & \textbf{Senior Software Developer}\\
	& Subject Matter Expert for the MediationZone data transformation and preprocessing tool. Responsibilities include: 
	\begin{itemize}
		\item Providing MediationZone knowledge and support to the clients development team
		\item Engagement with the operators Business Analysts to define solution requirements
		\item Collaboration with operator’s staff and AgileTransactions development team to define most effective solution design
		\item Development of mediation configurations and delivery of final solutions
		\item High availability aggregation and consolidation of data
		\item DTK MediationZone plugin development and Java build environment automation
	\end{itemize}
\end{tabularx}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{January 2010 --- March 2014}\\
\gray Employer & \textbf{Radiología Digital Diagnostica}\\
\gray Job Title & \textbf{IT Engineer}\\
& Worked as a Senior Developer consultant working on a medical solution project for a Radiology clinic. Activities included requirements capture, development and delivery of a Radiology Information System that would work across three cities in in Baja California Mexico using Java based technologies.
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{November 2006 --- January 2011}\\
\gray Employer & \textbf{International Rectifier Manufacturing Plant}\\ %\hfill New York, USA\\
\gray Job Title & \textbf{Electrical Test Engineer}\\
& Worked on design and implementation of custom solutions for real-time electrical data analysis of semiconductor manufacturing process using Python based technologies. 
Worked on custom software solutions for manufacturing processing tracking and reporting of manufactured goods.
Primary responsibilities included managing and diagnosing a semiconductor electrical test process, performing tests on defects and reporting on engineering lot runs.
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{February 2005 --- November 2006}\\
\gray Employer & \textbf{PPH Industrial / Wiremold} \\ %\hfill Amsterdam, The Netherlands\\
\gray Job Title & \textbf{JIT Coordinator}\\
& Lead small to medium size teams as the lead Just In Time coordinator in continuous improvement projects known as Kaizen events so we could implement improvements to the manufacturing process. This consisted in week long activities such as evaluation, implementation and measurement of proposed solutions by the team members.
I also developed an inventory reporting and product tracking system which was used during the company's monthly inventory evaluation.
\end{tabularx}


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{August 2008 --- November 2013}\\
\gray Degree & \textbf{Masters in Science in Telecommunications}\\
\gray University & \textbf{Universidad Autónoma de Baja California} \hfill Tijuana, México\\
%& Extra information about degree
& Thesis: Analysis of the performance of the USRP platform using the QPSK modulation scheme as a tool for teaching telecommunications.\\
& Project Description: Analyse the performance of the Universal Software Radio Peripheral as a tool for the study of digital modulation techniques and the software defined radio concept at an academic level.
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{January 1999 -- August 2004}\\
\gray Degree & \textbf{B.S. in Electrical Engineering}\\
\gray University & \textbf{Universidad Autónoma de Baja California} \hfill Tijuana, México\\
%& Extra information about degree
& Career focus in digital electronics and embedded systems.\\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------

\section{Languages}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Native & Spanish\\
Foreign & English 95\% written and spoken
\end{tabular}

%----------------------------------------------------------------------------------------
%	CONTACTS
%----------------------------------------------------------------------------------------

\section{Contacts}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Claudia Licet Huerta Zarate & Trainer ---  (664) 225-1170 \\
Javier Hernández Martínez & Electrical Engineer --- (664) 357-8940 \\
Luis Eduardo Rendón & Software Engineer --- (664) 188-8106 \\
Raymundo Miranda & Electronics Engineer --- (664) 121-5202
\end{tabular}

%----------------------------------------------------------------------------------------

\end{center}

\end{document}